---
title: "HanhPhan_DATA300_Lab2"
output: html_document
---
PART 1:

Use the c (combination) function to create a vector of elements 3, 5, 7, 11, 13
```{r}
myvector <- c(3, 5, 7, 11, 13)
myvector

```
Calculate the mean of the numbers using the mean() function
```{r}
mean(myvector)
```
Get the number of elements in the vector using the length() function
```{r}
length(myvector)
```



PART 2:

Import the dataset in the csv file and name it "mydata"
```{r}
mydata <- read.csv("traffic_survey_data.csv")
mydata
```
Print the car type of everyone who took the survey. The list is named car_list
```{r}
car_list <- mydata$cartype
car_list
```
Calculate the mean age of people who took the survey. Use na.rm to remove the NA values.
```{r}
mean_age <- mean(mydata$age,na.rm=TRUE)
mean_age
```

Summarize the age and education level of people who took the survey using the summary() function
```{r}
summary(mydata$age)
summary(mydata$education)
```

Get the total number of people who took the survey by getting the number of rows in the dataset
```{r}
num_pp <- nrow(mydata)
num_pp
```

