---
title: "DATA300_LAB3_HanhPhan"
output: html_document
---
```{r}
mydata <- read.csv("dataset.csv")

```

Part 1
Run through every value in cartype, if the value is blank, replace it with "no car", otherwise just keep it the same as it was.
```{r}
mydata$cartype <- ifelse(mydata$cartype=="","no car",mydata$cartype)
```

Part 2
Create a new variable called independent. If the respondent is not Democrat (democrat=0) and not Republican (GOP=0), then set the independent value to 1, otherwise set it to 0

```{r}
mydata$independent <- ifelse(mydata$democrat==0 & mydata$GOP==0,1,0)
mydata$independent
summary(mydata)
```
Part 3
Drop the subjectid column and change the column names to be informative
Use stargazer to create a table of summary statistics.
```{r results="asis"}
library(stargazer)

drop <- c("subjectid")
df = mydata[,!(names(mydata)%in%drop)]
colnames(df) <- c("Cartype","Education","Age","Urban","Married","Kids","Black","Female","Democrat","GOP","Bush Approval","Independent")

stargazer(df, type="html",title="Traffic Survey Data - Summary Statistic Table", column.sep.width = "15pt")


```
Part 4:
Create a table of 2 variables: cartype and bushapproval.
The table shows that most people who pickup seem to support President Bush (144 supported and 61 didn't). Approximately a half of car, no car, and SUV drivers supported President Bush and the other half didn't.

```{r}
table(mydata$cartype, mydata$bushapproval)
```



