---
title: "DATA300_Lab7_HanhPhan"
output: html_document
---

Part 1:
College_Grad is the variable with higher level of support for legalization. Female, Age, and Conservative are associated with lower levels of support for legalization. College_Grad is not statistically significant; other effects are statistically significant.
```{r}
library(ggplot2)

mydata <- read.csv("legalization_survey.csv")
#create a model for binary outcomes
m <- glm(legalize ~ age + conservative + female + college_grad,data=mydata, family="binomial",na.action = "na.exclude")

#get the confidence intervals
ci <- confint(m)

#create a data frame for the fit values and CI values
results <- data.frame(ci)
results$Estimate <- m$coefficients
results$List <- c("Intercept","Age","Conservative","Female","College Grad")
colnames(results) <- c("lwr","upr","Estimate","List")

#remove the Intercept line
results <- results[-c(1),]


#make a plot from that data frame
G <- ggplot(results,aes(y=List, x=Estimate)) +geom_point() + geom_errorbar(aes(xmin=lwr,xmax=upr),width=.4)
G <- G + labs(title="The Estimated Effect of Different Elements towards Marijuana Legalization", y="")+theme(plot.title = element_text(face="bold",size =12)) 
G

```


Part 2:
Age has a significant effect on the predicted probability of supporting legalization. The younger people are, the more they support marijuana legalization. Also, the plot implies that people who are non-conservative are more supportive of marijuana than those who are conservative.
```{r}
#create a new dataset where age varies from the lowest age value in the survey to the highest value. Conservative varies between 0 and 1, female is set to 1 and college_grad os set to 0
data2 <- expand.grid(age=seq(min(mydata$age,na.rm=T),max(mydata$age,na.rm=T)),conservative=c(0,1),female=1,college_grad=0)

#generate predictions with 95% confidence intervals
predictions <- predict(m,newdata=data2,type="response",se.fit=T)
predictions <- data.frame(fit=predictions$fit, lwr=predictions$fit-1.96*predictions$se.fit, upr=predictions$fit+1.96*predictions$se.fit)

#combine our new data set with predictions
predictions <- cbind(data2,predictions)

#plot the predictions and add the 95% CI to the plot
G2 <- ggplot(predictions,aes(x=age,y=fit,group=conservative,fill=as.factor(conservative))) + geom_line() + geom_ribbon(aes(x=age,y=fit,ymin=lwr,ymax=upr),alpha=.4) + scale_fill_manual(labels = c("Non-Conservative", "Conservative"), values = c("#4682B4", "#CD3700"))

#adjust the label names
G2 <- G2 + labs (title="Predicted probability of supporting marijuana legalization across \nthe range of age, for both conservatives and non-conservatives", x="Age", y="Probability of Legalization",fill="Politically conservative?") +theme(plot.title = element_text(face="bold"))
G2
```

