---
title: "DATA300_Lab8_HanhPhan"
output: html_document
---

Part 1: Carbon Emissions per Capita
I choose to color a country  with high carbon emission per capita red because it's polluted & against green. I color the panel background blue because it's similar to the color of water.

```{r}
library(maps)
library(ggplot2)
library(dplyr)
mydata <- read.csv("emissions_world_2019.csv")

#fix the country names in our data that aren't similar to the names in map_data
mydata$country <- ifelse(mydata$country=="United States","USA",mydata$country)
mydata$country <- ifelse(mydata$country=="United Kingdom","UK",mydata$country)
mydata$country <- ifelse(mydata$country=="Cote d'Ivoire","Ivory Coast",mydata$country)
mydata$country <- ifelse(mydata$country=="Congo","Republic of Congo",mydata$country)
mydata$country <- ifelse(mydata$country=="Democratic Republic of Congo","Democratic Republic of the Congo",mydata$country)
mydata$country <- ifelse(mydata$country=="Czechia","Czech Republic",mydata$country)

#calculate the CO2 per capita
mydata$co2percap <- mydata$co2/mydata$population

#join the two datasets
world_map <- map_data("world")
world_map <- left_join(world_map,mydata,by=c("region"="country"))

#make the plot
map1 <- ggplot(world_map,aes(x=long,y=lat,group=group)) + geom_polygon(aes(fill=co2percap),color="black",size=.1) + scale_fill_gradient2(low ="#fcf3e6", mid="#f5d4a6",  high = "#a30c02",midpoint=5, space = "Lab", na.value = "grey70", guide = "colourbar", aesthetics = "fill") + theme_void()

#add names for title and legend
map1 <- map1 + labs (title="Map of Carbon Emissions per Capita",x=" ",y=" ", fill="CO2 per capita") +theme(plot.title = element_text(face="bold",hjust=0.5)) + theme(legend.position = "bottom") + theme(panel.background = element_rect(fill = "#aec8eb"))
map1

```



Part 2: Energy Sources

I tried to choose the color of energy sources based on the color that relates to the energy's colors (renewable, gas). But not all of them had a representative color in real life, so I chose what I think would look like instead. I color the panel background blue because it's similar to the color of water. I also got rid if the legend's name because I think the title says it all.


```{r}
#make the plot
map2 <- ggplot(world_map,aes(x=long,y=lat,group=group)) + geom_polygon(aes(fill=as.factor(source)),color="black",size=.1)  + theme_void()

#adjust the color
map2 <- map2 +scale_fill_manual( values = c( "#36454f", "#FDFF46", "#B22222", "#A17917", "#0ee31f"),na.value = "grey70") 

#add title and theme
map2 <- map2 + labs (title="Most Popular Energy Sources",x=" ",y=" ",fill="")
map2 <- map2 + theme(
  plot.title = element_text(face="bold",hjust=0.5),
  legend.position = "bottom", 
  panel.background = element_rect(fill = "#aec8eb"), 
  legend.box="horizontal",
  legend.key.size = unit(0.5,"cm"),
  )
map2
```

